---
title: "R Studies - 2. Lab Introduction to R"
output: html_notebook
---
This notebook is a set of studies for the book "An Introduction To Statistical Learning - second Edition". The series of notebooks start at the second chapter - Statistical Learning - since the first chapter does not have any R exercises.

Before starting, R can be downloaded from 
<center><http://cran.r-project.org>.</center>
This notebook is written and build using RStudio, which can be freely downloaded from

<center><http://rstudio.com>.</center>

## 2.3.1 Basic Commands
The following command instructs R to join together the numbers 1, 2, 3, and 5, and to save them as a vector named **x**. When we type **x**, it gives us back the vector.
```{r}
x <- c(1,3,2,5)
x
```

We can also save things using **=** rather than **<-**:
```{r}
x = c(1,6,2)
y = c(1,4,3)
c(x,y)
```
In additions, typing **?funcname** will cause R to open a new help file window with additional information about the function **funcname()**.
We can check a variable length using the **length()** function.
```{r}
length(x)
length(y)
x+y
```
The **ls()** function allow us to look at a list of all of the objects, such as data and functions, that we have saved so far. The **rm()** function can be used to delete any that we don't want.
```{r}
ls()
rm(x,y)
```
And is also possible to remove all objects at once:
```{r}
rm(list=ls())
```
The **matrix()** function will be essencial to use algebra in our statistical learning. The function takes a **data** parameter and a number os rows and columns that will compose the matrix.
```{r}
x <- matrix(data = c(1,2,3,4),nrow = 2, ncol = 2)
x
```
We don't need to specify the name of the parameters once that we put them in the correct order.
```{r}
x <- matrix(c(1,2,3,4),2,2)
x
```
By default **R** creates matrices by successively filling in columns. Alternativelty the **byrow = TRUE** option can be used to populate the matrix in order of the rows.
```{r}
matrix(c(1,2,3,4),2,2,byrow = TRUE)
```
We can get the square root of a number, a vector or a matrix with the function **sqrt()**.
```{r}
sqrt(x)
```
Similarly, we can get the value of each element powered by two:
```{r}
x^2
```
The **rnorm()** function generates a vector of random normal variables, with first argument **n** the sample size. Each time we call this function, we will get a different answer.
```{r}
x<-rnorm(50)
x;
```
We create two correlated sets of numbers, **x** and **y**, and use the **cor()** function to compute the correlation between them.
```{r}
y <- x + rnorm(50,mean=50, sd = .1)
cor(x,y)
```
We can set the a seed to reproduce the exact same set of random numbers: we can use the **set.seed()** function to do this.
```{r}
set.seed(1303)
rnorm(50)
```
The **mean()** and **var()** functions can be used to compute the mean and variance of a vector of numbers. We can apply **sqrt()** after the **var()** function to have the standard deviation or simply use the **sd()** function.

```{r}
set.seed(3)
y <- rnorm(100)
cat("Mean:",mean(y),"\nVar:",var(y),"\nSqrt(Var):",sqrt(var(y)),"\nStandard Deviation:",sd(y))
```
## 2.3.2 Graphics


### References
1. James, G.; Witten, D.; Hastie, T.; Tibshirani, R. **An Introduction to Statistical Learning - Second Edition**. Springer, 2021.
