---
title: "R Studies - 2. Lab Introduction to R"
output: html_notebook
---
This notebook is a set of studies for the book "An Introduction To Statistical Learning - second Edition". The series of notebooks start at the second chapter - Statistical Learning - since the first chapter does not have any R exercises.

Before starting, R can be downloaded from <http://cran.r-project.org>. This notebook is written and build using RStudio, which can be freely downloaded from
\<center><http:rstudio.com><\center>

## 2.3.1 Basic Commands
The following command instructs R to join together the numbers 1, 2, 3, and 5, and to save them as a vector named **x**. When we type **x**, it gives us back the vector.
```{r}
x <- c(1,3,2,5)
x
```

We can also save things using **=** rather than **<-**:
```{r}
x = c(1,6,2)
y = c(1,4,3)
c(x,y)
```
In additions, typing **?funcname** will cause R to open a new help file window with additional information about the function **funcname()**.
We can check a variable length using the **length()** function.
```{r}
length(x)
length(y)
x+y
```
```{r}
ls()
rm(x,y)
```
```{r}
rm(list=ls())
```

### References


Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

